\documentclass[]{style}

\begin{document}

\header{Sacha}{ Goldman}{} % Subtitle

\vspace{-5mm}
\begin{center}
	\textbf{Email}
%	\url{mailto:sacha@sachagoldman.com}{sacha@sachagoldman.com} \hspace{1cm}
	\url{mailto:sacha.goldman@mail.utoronto.ca}{sacha.goldman@mail.utoronto.ca} \hspace{1cm}
	\textbf{Website} 
	\url{https://sachagoldman.com}{sachagoldman.com}
\end{center}
\vspace{5mm}
 
\section{Education}

\begin{entrylist}

\vspace{1mm}

\entry
{PhD in Mathematics \ {\normalfont \underline{University of Toronto}}}
{September 2023 – }
{  ~ \vspace{-2.5mm}

Supervised by Alexander Kupers.
}

\entry
{MSc in Mathematics \ {\normalfont \underline{University of Toronto}}}
{September 2023 – September 2024}
{  ~ \vspace{-2.5mm}

Supervised by Alexander Kupers. Thesis: Properties of Automorphisms of Spaces with Cyclic-by-Finite Fundamental Group
}

\vspace{-3mm}
\entry{BSc in Mathematics and Computer Science \ {\normalfont \underline{University of Toronto}}}
{September 2019 – June 2023}
{}

\end{entrylist}

\section{Papers and Preprints}

\begin{entrylist}

\vspace{1mm}

\entry
{The Torsion of Automorphisms of Nilpotent Spaces \ {\normalfont \underline{\href{https://arxiv.org/abs/2601.14988}{arXiv}}}}
{January 2026}
{}

\end{entrylist}

\vspace{-3mm}

\section{Awards}

\begin{entrylist}

\vspace{-3mm}
\entry
{Ontario Graduate Scholarship \ {\normalfont \underline{Province of Ontario}}}
{2025 – 2026}
{}

\vspace{-3mm}
\entry
{Canadian Graduate Scholarship – Master's \ {\normalfont \underline{National Sciences and Engineering Research Council}}}
{2024 – 2025}
{}

\vspace{-3mm}
\entry
{Coxeter Scholarship in Mathematics \ {\normalfont \underline{University of Toronto}}}
{2024}
{}

\vspace{-3mm}
\entry
{Undergraduate Summer Research Award \ {\normalfont \underline{National Sciences and Engineering Research Council}}}
{2023}
{}

\vspace{-3mm}
\entry
{Raptors Foundation In-Course Scholarship \ {\normalfont \underline{New College}}}
{2023}
{}

\vspace{-3mm}
\entry
{In-Course Scholarship \ {\normalfont \underline{New College}}}
{2022}
{}

\vspace{-3mm}
\entry
{In-Course Scholarship \ {\normalfont \underline{New College}}}
{2021}
{}

\vspace{-3mm}
\entry
{William and Shirley Reed Scholarship \ {\normalfont \underline{VSB}}}
{2019}
{}

\end{entrylist}

\section{Teaching}

\begin{entrylist}

\vspace{1mm}

\entry
{MAT257 Teaching Assistant \ {\normalfont \underline{University of Toronto}}}
{September  2024 – April 2026}
{ ~ \vspace{-2.5mm}

Running tutorials, holding office hours, and grading for a course covering calculus on manifolds. 
}

\entry
{MAT1300 Teaching Assistant \ {\normalfont \underline{University of Toronto}}}
{September  2024 – December 2024}
{ ~ \vspace{-2.5mm}

Grading for a graduate course on differential topology.
}

\entry
{MAT185 Teaching Assistant \ {\normalfont \underline{University of Toronto}}}
{January  2024 – April 2024}
{ ~ \vspace{-2.5mm}

Running tutorials and grading for a proof based linear algebra course.
}

\entry
{Math Learning Centre Teaching Assistant \ {\normalfont \underline{University of Toronto}}}
{January  2024 – April 2024}
{ ~ \vspace{-2.5mm}

Helping students at the math learning centre.
}

\entry
{MAT186 Teaching Assistant \ {\normalfont \underline{University of Toronto}}}
{September 2023 – December 2023}
{ ~ \vspace{-2.5mm}

Running tutorials and grading for a differential and integral calculus course.
}

\entry
{CSC236 Teaching Assistant \ {\normalfont \underline{University of Toronto}}}
{September 2021 – December 2021}
{ ~ \vspace{-2.5mm}

Running tutorials and grading for a course introducing mathematics for computer science.
}

\end{entrylist}

\section{Speaking}

\begin{entrylist}

\vspace{1mm}

\entry
{Birds Eye Conference \ {\normalfont \underline{University of Toronto}}}
{2026}
{ ~ \vspace{-2.5mm}

An expository talk about Configuration spaces and braid groups.}

\entry
{Synthetic Spectra Learning Seminar \ {\normalfont \underline{University of Toronto}}}
{2025}
{ ~ \vspace{-2.5mm}

An expository talk about Patchkoria–Pstr\k{a}gowski's proof of Franke's algebracity conjecture.}

\entry
{Locally Trivial Seminar \ {\normalfont \underline{University of Toronto}}}
{2025}
{ ~ \vspace{-2.5mm}

A talk about ongoing joint work with Jonathan Sejr Pedersen and Marco Volpe studying signatures of manifold bundles.}

\entry
{Local Systems and Simple Homotopy Thoery \ {\normalfont \underline{Young Homotopy Theorists Meeting}}}
{2025}
{ ~ \vspace{-2.5mm}

A poster about work, partially joint with Marco Volpe, on simple homotopy theory using local systems of spectra.}

\entry
{Summer Kan Seminar \ {\normalfont \underline{University of Toronto}}}
{2025}
{ ~ \vspace{-2.5mm}

An expository talk about the Sullivan conjecture.}

\entry
{Simple Homotopy Week \ {\normalfont \underline{University of Toronto}}}
{2025}
{ ~ \vspace{-2.5mm}

Two talks, one on Waldhausen's construction of the assembly map and the other on a proof of the topological Dwyer-Weiess-Williams theorem.}

\entry
{Locally Trivial Seminar \ {\normalfont \underline{University of Toronto}}}
{2025}
{ ~ \vspace{-2.5mm}

Speaking about local systems in geometric topology, specifically relating to the Euler characteristic, the Wall finiteness obstruction, and the Whitehead torsion.}

\entry
{Cohomology of the General Linear Group Learning Seminar \ {\normalfont \underline{University of Toronto}}}
{2024}
{ ~ \vspace{-2.5mm}

An expository talk about the $K$-theory of finite fields.}

\entry
{Ontario Graduate Mathematics Conference \ {\normalfont \underline{University of Waterloo}}}
{2024}
{ ~ \vspace{-2.5mm}

Speaking about finiteness properties of some automorphism groups of manifolds.}

\entry
{Birds Eye Conference \ {\normalfont \underline{University of Toronto}}}
{2024}
{ ~ \vspace{-2.5mm}

An expository talk about rational homotopy theory and Sullivan's minimal models.}

\entry
{Graduate Student Seminar \ {\normalfont \underline{University of Toronto}}}
{2024}
{ ~ \vspace{-2.5mm}

An expository talk about the calculation of homotopy groups of spheres.}

\entry
{Canadian Undergraduate Mathematics Conference \ {\normalfont \underline{University of Toronto}}}
{2023}
{ ~ \vspace{-2.5mm}

An expository talk about using the Hopf fibration to calculate $\pi_3(S^2)$.}

\end{entrylist}

\section{Service}

\begin{entrylist}

\vspace{1mm}

\entry
{Locally Trivial Seminar \ {\normalfont \underline{University of Toronto}}}
{January 2025 – }
{ ~ \vspace{-2.5mm}

A student seminar I started with Jonathan Pedersen on topics loosely related to algebraic topology.}

\entry
{Readings on Signatures of High-Dimensional Knots \ {\normalfont \underline{Directed Reading Program}}}
{January 2026 – April 2026}
{ ~ \vspace{-2.5mm}

Supervising a group of undergraduate students reading about high dimensional knots and signatures of knots.}

\entry
{Readings on Topological $K$-Theory \ {\normalfont \underline{Directed Reading Program}}}
{January 2025 – April 2025}
{ ~ \vspace{-2.5mm}

Supervising a group of undergraduate students reading about topological $K$-theory and the Hopf invariant one problem.}

\entry
{Graduate Student Seminar Organizer \ {\normalfont \underline{Math Graduate Student Association}}}
{September 2024 – August 2025}
{ ~ \vspace{-2.5mm}

Organizing the University of Toronto's mathematics graduate student seminar.}

\entry
{Academic Committee \ {\normalfont \underline{Math Graduate Student Association}}}
{September 2023 – August 2024}
{ ~ \vspace{-2.5mm}

Helping to organize academic events and the graduate student seminar.}

\end{entrylist}

\newpage

\section{Employment}

\begin{entrylist}

\vspace{1mm}

\entry
{Software Engineer Intern \ {\normalfont \url{https://www.apple.com}{Apple}}}
{May 2022 – August 2022}
{ ~ \vspace{-2.5mm}

Worked on the team architecting Apple Media Apps solving unique technical challenges. }

\entry
{Software Developer Intern \ {\normalfont \url{https://www.ssense.com}{SSENSE}}}
{May 2021 – August 2021}
{ ~ \vspace{-2.5mm}

Worked on the iOS team facilitating a transition to the composable architecture and SwiftUI.}

\entry
{Software Developer Intern \ {\normalfont \url{https://altairix.com}{Altairix}}}
{May 2020 – August 2020}
{ ~ \vspace{-2.5mm}

Worked on the web based learning platform for students with disabilities.}

\end{entrylist}

\section{Misc}

\begin{entrylist}

\vspace{1mm}

\textbf{Canadian Citizen}\\

\textbf{American Citizen}

\end{entrylist}

\end{document}